---
title: "Lab 3"
author: "Allegra, Rosie, Fay"
date: "2024-02-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Lab 3


```{r}
library(ggplot2)
library (tidyverse)
load("~/CCNY 2024/2023-2024/PSY V0500 Stats/Statting/BRFSS2022/BRFSS2022_rev.RData")
```
```{r}
brfss22$Age_midpt <- fct_recode(brfss22$X_AGEG5YR, "21" = "Age 18 to 24", "27" = "Age 25 to 29", "32" = "Age 30 to 34", "37" = "Age 35 to 39", "42" = "Age 40 to 44", "47" = "Age 45 to 49", "52" = "Age 50 to 54", "57" = "Age 55 to 59", "62" = "Age 60 to 64", "67" = "Age 65 to 69", "72" = "Age 70 to 74", "77" = "Age 75 to 79", "82" = "Age 80 or older", NULL = "Don't know/Refused/Missing")

brfss22$Age_midpt <- as.numeric(levels(brfss22$Age_midpt))[brfss22$Age_midpt]
```

```{r}
select_tristate <- (brfss22$X_STATE == "New York") | (brfss22$X_STATE == "New Jersey") | (brfss22$X_STATE == "Connecticut")
brfss_tristate <- subset(brfss22,select_tristate)
```

```{r}
p_tri <- ggplot(data = brfss_tristate,
                mapping = aes(x = Age_midpt, 
                              y = X_BMI5))
p_tri + geom_smooth()

```

```{r}
p_tri + geom_jitter(width = 2.5, height = NULL, alpha = 0.05)

```

```{r}
p_tri <- ggplot(data = brfss_tristate,
                mapping = aes(x = Age_midpt,
                              y = X_BMI5,
                              color = X_STATE,
                              fill = X_STATE))
p_tri + geom_smooth()
```

```{r}
ACEdidntask <- (as.numeric(is.na(brfss22$ACEDEPRS)) + 
                        as.numeric(is.na(brfss22$ACEDRINK)) +
                        as.numeric(is.na(brfss22$ACEDRUGS)) +
                        as.numeric(is.na(brfss22$ACEPRISN)) +
                        as.numeric(is.na(brfss22$ACEDIVRC)) +
                        as.numeric(is.na(brfss22$ACEPUNCH)) +
                        as.numeric(is.na(brfss22$ACEHURT1)) +
                        as.numeric(is.na(brfss22$ACESWEAR)) +
                        as.numeric(is.na(brfss22$ACETOUCH)) )
select_ACE <- (ACEdidntask == 0) # with zero missing values for any of ACE questions
brfss_ACE <- subset(brfss22, select_ACE)
```

```{r}
xtabs(~ brfss_ACE$ACEDRINK + brfss_ACE$ACEDRUGS)
```

```{r}
ftable(xtabs(~ brfss_ACE$ACEDRINK + brfss_ACE$ACEDRUGS))
```

```{r}
brfss_ACE$ACEDRINK_recode <- fct_recode(brfss_ACE$ACEDRINK,
                                         "Yes" = "Yes, Adverse Childhood Exper, lived with someone who was a problem drinker or alcoholic",
                                "No" = "No", 
                                "Not sure" = "dont know not sure",
                                "Refused" = "refused")
summary(brfss_ACE$ACEDRINK_recode)
```
```{r}
summary(brfss22$ACEDRUGS)
```



```{r}
brfss_ACE$ACEDRUGS_recode <- fct_recode(brfss_ACE$ACEDRUGS,
                                         "Yes" = "Yes, Adverse Childhood Exper, lived with someone who used illegal street drugs or who abused prescription medications",
                                "No" = "No", 
                                "Not sure" = "dont know not sure",
                                "Refused" = "refused")
summary(brfss_ACE$ACEDRUGS_recode)
```
```{r}
p_acesubst <- ggplot(data = brfss_ACE,
                     mapping = aes(x = brfss_ACE$ACEDRINK_recode,
                                   y = brfss_ACE$ACEDRUGS_recode))
p_acesubst + geom_point()

##To be honest I'm not totally sure what I was expecting to see in this plot. I'm going to look into the appendix of Lab 3 and recode some more ACE data and then try another graph.
```


```{r}
summary(ACEdidntask)
quantile(ACEdidntask, probs = c(0.01,0.05,0.1,0.15,0.2))

## There are 9 different subsets of the ACE survey (drinks, drugs, depression, etc.). The ACEdidntask value set has been coded numerically so that a response of NA = yes is a 1, and a NA = no is a 0. If the subject responded NA to none of the ACE questions (meaning they answered all of them), they would have a value of 0 for ACEdidntask. If the subject responded NA to all 9 questions, they would have a value of 9 for ACEdidntask.
```
```{r}
##Therefore, from the above output, we can conclude that between 10 and 15% of respondents answered all 9 questions in the ACE set. So let's narrow that down further, for fun.

quantile(ACEdidntask, probs = c(0.1,0.11,0.12,0.13,0.14,0.15))
```

```{r}
##One more, for luck:

quantile(ACEdidntask, probs = c(0.101,0.102,0.103,0.104,0.105,0.106,0.107,0.108,0.109,0.11))

##Interestingly, this breakdown shows that while a vast majority of people were asked either all 9 ACE questions or none of the ACE questions, a few respondents were asked between 9 and 0 of the ACE questions.
```

```{r}
summary(brfss22$ACEPRISN)

brfss_ACE$ACEPRISN_recode <- fct_recode(brfss_ACE$ACEPRISN,
                                         "Yes" = "Yes, Adverse Childhood Exper, lived with someone who served time or was sentenced to serve time in a prison, jail, or other correctional facility",
                                "No" = "No", 
                                "Not sure" = "dont know not sure",
                                "Refused" = "refused")
summary(brfss_ACE$ACEPRISN_recode)
```

```{r}
summary(brfss_ACE$ACEDRINK_recode)
summary(brfss_ACE$ACEDRUGS_recode)
summary(brfss_ACE$ACEPRISN_recode)
```
##ACEDRINK total: 47972, % yes = 23.91
##ACEDRUGS total: 47972, % yes = 9.72
##ACEPRISN total: 47972, % yes = 7.35

Ideas to consider testing:
What is the most common kind of ACE?
How much greater, proportionately, is that ACE to the other ACEs?

Note that the xtabs command (search Lab3 for code bits) will do cross tabs of the two variables: one set will be X and one will be Y, and you read it like a table

```{r}
xtabs(~ brfss_ACE$ACEDRINK_recode + brfss_ACE$ACEDRUGS_recode)
ftable(xtabs(~ brfss_ACE$ACEDRINK_recode + brfss_ACE$ACEDRUGS_recode))
```
## Notes: Use those tables to calculate the marginal & conditional probabilities (see lectures week 3). Then do a hypothesis test to see if those probabilities are the same (spoiler: they aren't). Example, 3/11 and 8/11 vs 1.5/35.5 and 34/35.5 , horizontal marginals. Also try vertical.

## For HW, try re-recoding so that DKNS and refused become yes or no, see if that affects the stats significantly. Note that some ACE questions might have more complex answers, like SWEAR: never vs once vs more than once. Realize that simplifying will make the tables simpler.

## Test likelihoods such as ACE + depression diagnosis

```{r}
## To take a look at the overlaps/intersections of multiple ACE factors, finish filling in these codes:

brfss_ACE$ACEmultiple <- (as.numeric(brfss_ACE$ACEDRINK_recode == "Yes") + 
                  )

summary(brfss_ACE$ACEmultiple)

## This will tell you how many people answered yes to how many of the ACE subset

xtabs(~ brfss_ACE$ACEmultiple + )

## The xtabs for ACEmultiple and another ACE dimension will help narrow down how many people from each subset of the ACE have tagged how many of the ACE dimensions

```




