---
title: "Lab4_knn_datamanip"
author: "Allegra Durante"
date: "2024-03-07"
output: html_document
---


This is part 2 of my HW5, picking up where Lab4 left off.


```{r}
load("~/CCNY 2024/2023-2024/PSY V0500 Stats/Statting/BRFSS2022/BRFSS2022_rev.RData")
library(tidyverse)
library(ggplot2)
library(gapminder)
require(class)
require(caret)
```

This shows there are categories INCOME3 for income and SLEPTIM1 for income and sleep time, I'm curious if there's a correlation between the two. I've been watching a few videos on statistics in R, so I'll be using some commands that haven't come up in class before.

## My hypothesis is that people with lower income sleep less than people with higher income.

```{r}
glimpse(brfss22)
```



```{r}
attach(brfss22)
summary(SLEPTIM1)
table(SLEPTIM1)
summary(INCOME3)
table(INCOME3)
```

```{r}
brfss22$income_max <- fct_recode(brfss22$INCOME3, "10" = "Household income less than $10,000",
                                "15" = "Less than $15,000 ($10,000 to less than $15,000)", 
                                "20" = "Less than $20,000 ($15,000 to less than $20,000) ",
                                "25" = "Less than $25,000 ($20,000 to less than $25,000) ",
                                "35" = "Less than $35,000 ($25,000 to less than $35,000) ",
                                "50" = "Less than $50,000 ($35,000 to less than $50,000) ", 
                                "75" = "Less than $75,000 ($50,000 to less than $75,000)",
                                "100" = "Less than $100,000 ($75,000 to less than $100,000)",
                                "150" = "Less than $150,000 ($100,000 to less than $150,000)",
                                "200" = "Less than $200,000 ($150,000 to less than $200,000)",
                                "201" = "$200,000 or more",
                                NULL = "Dont know/Not sure", NULL = "Refused", NULL = "NA's")
```

```{r}
summary(X_AGEG5YR)
summary(brfss22$income_max)
```
Visualizing:
```{r}
attach(brfss22)
hist(income_max)
```
Trying again, since I need to change income_max to numeric:
```{r}
glimpse(brfss22)
as.numeric(income_max)
```
That didn't do it, so let's keep trying
```{r}
income_num <- (as.numeric(income_max))
glimpse(brfss22)
```
So now income_num is a value set of numbers but it's not part of brfss22 any more. I think that's ok. Trying those visualizations again:
```{r}
hist(income_num)
hist(SLEPTIM1)
```
Keeping going
```{r}
  ggplot(aes(x=income_num, y=SLEPTIM1))+
  geom_point()
```

# I ran out of time to work on this at this point because I have to catch a plane tonight, but I think I'm starting to understand how to work with data in R and try things.



